Pesticides pollution of small streams in Germany

### 2016-07-27 article.tex

We queried chemical monitoring data of pesticides from sampling sites with catchment size $\mathrm{< 100km^2}$ for the years 2005 to 2015 from all 13 non-city federal states of Germany.
Additionally, we compiled data available from previous studies and searched online databases.
This yielded to a total of more then 30 datasets of different formats.

@@

The compiled dataset comprised only few standing waters (58 sites) and the majority (90\%) of samples where taken via grab sampling.  % see clean.R for numbers
Therefore, we report only results of grab samples from streams. 
The analysed dataset comprised 42899 samples from 3049 sampling sites (Figure \ref{fig:fig1} and Supplement, Table \todo{Set ref to table}). 
We found big differences in the number of sampling sites between federal states.

484 compounds that could be classified as pesticides and their metobalites (Supplement, Table \todo{Set ref to table}) .

@@

\begin{figure}
  \includegraphics[width=.8\textwidth]{fig/ezg_lu.pdf}
  \caption{Distribution of catchment area and agriculture within the catchment area across the sampling sites.
  Only sampling sites with catchment area < 150 km\textsuperscript{2} are displayed. 
  Colour codes the 2-dimensional density of points.
  }
  \label{fig:fig_ezg_lu}
\end{figure}

>>>>

We queried chemical monitoring data of pesticides from sampling sites with catchment size $\mathrm{< 100km^2}$ for the years 2005 to 2015 from all 13 non-city federal states of Germany.
Additionally, we compiled data available from previous studies and searched online databases.
This yielded to a total of more then 30 datasets of different formats.
In the following we will use the ISO 3166-2:DE standard abbreviations for federal states.

@@

The compiled dataset comprised only few standing waters (58 sites) and the majority (90\%) of samples where taken via grab sampling.  % see clean.R for numbers
Therefore, we report only results of grab samples from streams. 
The analysed dataset comprised 42236 samples from 3049 sampling sites.  %see do_overview.R for numbers.
We found big differences in the number of sampling sites between federal states (Figure \ref{fig:fig1} and Supplement, Table \todo{Set ref to table}).

@@

In total 484 different compounds that could be classified as pesticides and their metobalites were measured at least once (Supplement, Table \todo{Set ref to table}). 
Most of the compounds were herbicides (179), followed by insecticides (117) and fungicides (109).
We found substantial differences of the spectra of analysed compounds (Figure \ref{fig:figvar}).
Hierarchical clustering revealed three groups of states:
i) with less then 100 compounds (SL, ST and TH), ii) with a medium sized spectra and iii) with a big and distinct spectra (RP and NI).
Only 5\% of the samples were taken at or after days with rainfall events greater than 10mm / day.

\begin{figure}
  \includegraphics[width=\textwidth]{fig/figvar.pdf}
  \caption{Compound spectra of the different federal states. Left: Barcode plot - Each vertical line is an analysed compound. Right: MDS ordination. 
  Colors according to three groups determined by hierarchical clustering (see Supplement Figure (xxx).}
  \label{fig:figvar}
\end{figure}

The distribution of sampling sites across catchment area and agricultural area in the catchment revealed a sharp decline in the distribution of catchment-sizes below $10~km^2$, with most sampling sites with catchments between 10 and 25 $km^2$ (Figure \ref{fig:figezglu}).
The proportion of agriculture in the catchments decreased with increasing catchment size.

\begin{figure}
  \includegraphics[width=.8\textwidth]{fig/ezglu.pdf}
  \caption{Distribution of catchment area and agriculture within the catchment area across the sampling sites.
  Only sampling sites with catchment area < 150 km\textsuperscript{2} are displayed. 
  Colour codes the 2-dimensional density of points.
  }
  \label{fig:figezglu}
\end{figure}
